Supplementary tables and figures for "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-06-05 src/docs_paper/tables-figures.Rmd
Include gt in .yml and add table to .Rmd #128

\caption{All surveys that we used in our analysis.}

@@

>>>>

\caption{All surveys that we used in our analysis and their sample sizes.}

@@

\begin{longtable}{lrr}
\toprule
Country & Number of areas & Analysis level \\ 
\midrule
Botswana & 27 & 3 \\ 
Cameroon & 58 & 2 \\ 
Kenya & 47 & 2 \\ 
Lesotho & 10 & 1 \\ 
Mozambique & 161 & 3 \\ 
Malawi & 33 & 5 \\ 
Namibia & 38 & 2 \\ 
Eswatini & 4 & 1 \\ 
Tanzania & 195 & 4 \\ 
Uganda & 136 & 3 \\ 
South Africa & 52 & 2 \\ 
Zambia & 116 & 2 \\ 
Zimbabwe & 63 & 2 \\ 
\bottomrule
\end{longtable}
